Poseidon Adventure

### 2019-05-06 docs/index.Rmd
add comp testing to index

>>>>

Standard survey with composition sampling: impact of selectivity, `sample_fish`

<a href="https://sgaichas.github.io/poseidon-dev/StdSurvLengthAgeCompTest.html" target="_blank">Compare true cohort comp with survey + sampling - May 6, 2019</a>

<a href="https://sgaichas.github.io/poseidon-dev/NEUSStdSurvCohortCompTest.html" target="_blank">True cohort comp vs survey comparison NEUS - May 6, 2019</a>

<a href="https://sgaichas.github.io/poseidon-dev/CCAStdSurvCohortCompTest.html" target="_blank">True cohort comp vs survey comparison CCA - May 6, 2019</a>

<a href="https://sgaichas.github.io/poseidon-dev/NOBAStdSurvCohortCompTest.html" target="_blank">True cohort comp vs survey comparison NOBA - May 6, 2019</a>
